Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-18 paper/paper.tex
Include all images in the dissertation
Add to characterising the data set section

\title{Measuring Software Ticket Quality using Quantitative Data Analysis}
\author{Andrei-Mihai Nicolae}
\matricnum{2147392}

@@

In this research paper, we present and discuss our findings after running a quantitative data analysis 
on over 300,000 tickets taken from more than 15 open source projects. We have implemented a Go application 
with multiple commands (i.e. store, analyze, plot, statistics) that can automatically fetch any number of tickets 
from a Jira instance, analyze them, generate plots and run statistical tests.

During the analysis part, we investigate several variables in correlation with \emph{time-to-complete}, 
which we define as the \emph{metric of quality}. \emph{time-to-complete} represents the period of time between the creation 
and the closing of a ticket; more specifically, the creation of the ticket is marked when the status of the ticket is set to 
\emph{Open} and the closing of a ticket is considered when the ticket status is set to \emph{Closed} (or some similar status, 
such as \emph{Fixed}, \emph{Resolved}). \emph{Time-To-Complete} is our dependent variable, and as independent variables 
(i.e. variables controlled in order to test the effects on the dependent variable) we have set a number of ticket fields.

This study brings several contributions to the research community:
\begin{itemize}
  \item it is one of the very few research projects that investigates such a large number of tickets (over 300,000) spanning
  across a variety of projects (i.e. 21 projects);
  \item it is one of the few studies in the field that performs a quantitative analysis rather than a qualitative one;
  \item it is, to our knowledge, the first study to conduct sentiment and grammar correctness analyses on software tickets.
\end{itemize}

@@

Also, in order to validate our findings, the statistics command fetches all the data from the database and runs two types of 
tests: Welch's T Test \cite{welch1947generalization} for analysing categorical data (e.g. has/does not have attachments)
and Spearman's rank correlation coefficient \cite{spearman1904proof} for investigating continuous data (e.g. how do different 
grammar correctness scores change \emph{Time-To-Complete}).

@@

\subsection{Attachments}

\subsection{Comments}

\subsection{Summary and Description}

\subsection{Grammar Correctness}

\subsection{Sentiment Analysis}

\subsection{Steps to Reproduce}

\subsection{Stack Traces}

@@

% \begin{figure*}
% \begin{center}
% \includegraphics[scale=0.3]{images/alice.pdf}
% \end{center}
% \caption{\label{fig-eg}An example figure stretching over two columns}
% \end{figure*}

>>>>

\title{Measuring Software Ticket Quality using Quantitative Data Analysis}
\author{Andrei-Mihai Nicolae}
\matricnum{21473292}

@@

In this research paper, we present and discuss our findings after running a quantitative data analysis 
on over 3200,000 tickets taken from more than 15 open source projects. We have implemented a Go application 
with multiple commands (i.e. store, analyze, plot, statistics) that can automatically fetch any number of tickets 
from a Jira instance, analyze them, generate plots and run statistical tests.

During the analysis part, we investigate several variables in correlation with \emph{Time-To-Close}, 
which we define as the \emph{metric of quality}. \emph{Time-To-Close} represents the period of time between the creation 
and the closing of a ticket; more specifically, the creation of the ticket is marked when the status of the ticket is set to 
\emph{Open} and the closing of a ticket is considered when the ticket status is set to \emph{Closed} (or some similar status, 
such as \emph{Fixed}, \emph{Resolved}). \emph{Time-To-Close} is our dependent variable, and as independent variables 
(i.e. variables controlled in order to test the effects on the dependent variable) we have set a number of ticket fields.

This study brings several contributions to the research community:
\begin{itemize}
  \item it is one of the very few research projects that investigates such a large number of tickets (over 3200,000) spanning
  across a variety of projects (i.e. 21 projects);
  \item it is one of the few studies in the field that performs a quantitative analysis rather than a qualitative one;
  \item it is, to our knowledge, the first study to conduct sentiment and grammar correctness analyses on software tickets.
\end{itemize}

@@

Also, in order to validate our findings, the statistics command fetches all the data from the database and runs two types of 
tests: Welch's T Test \cite{welch1947generalization} for analysing categorical data (e.g. has/does not have attachments)
and Spearman's rank correlation coefficient \cite{spearman1904proof} for investigating continuous data (e.g. how do different 
grammar correctness scores change \emph{Time-To-Close}).

@@

\subsection{Attachments}
\begin{figure}
  \begin{center}
  \includegraphics[scale=0.2]{images/attachments.png}
  \end{center}
  \caption{\label{fig-eg}Application flow of the Go tool.}
  \end{figure}

\subsection{Comments}
\begin{figure}
  \begin{center}
  \includegraphics[scale=0.2]{images/comment_complexity.png}
  \end{center}
  \caption{\label{fig-eg}Application flow of the Go tool.}
  \end{figure}

\subsection{Summary and Description}
\begin{figure}
  \begin{center}
  \includegraphics[scale=0.2]{images/fields_complexity.png}
  \end{center}
  \caption{\label{fig-eg}Application flow of the Go tool.}
  \end{figure}

\subsection{Grammar Correctness}
\begin{figure}
  \begin{center}
  \includegraphics[scale=0.2]{images/grammar_correctness.png}
  \end{center}
  \caption{\label{fig-eg}Application flow of the Go tool.}
  \end{figure}

\subsection{Sentiment Scores}
\begin{figure}
  \begin{center}
  \includegraphics[scale=0.2]{images/sentiment_analysis.png}
  \end{center}
  \caption{\label{fig-eg}Application flow of the Go tool.}
  \end{figure}

\subsection{Steps to Reproduce}
\begin{figure}
  \begin{center}
  \includegraphics[scale=0.2]{images/steps_to_reproduce.png}
  \end{center}
  \caption{\label{fig-eg}Application flow of the Go tool.}
  \end{figure}

\subsection{Stack Traces}
\begin{figure}
  \begin{center}
  \includegraphics[scale=0.2]{images/stack_traces.png}
  \end{center}
  \caption{\label{fig-eg}Application flow of the Go tool.}
  \end{figure}

@@

% \begin{figure}
% \begin{center}
% \includegraphics[scale=0.32]{images/alice.pdf}
% \end{center}
% \caption{\label{fig-eg}An example figure stretching over two columns}
% \end{figure*}
